%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer II} % Job title
    {Flink} % Organization
    {Berlin, Germany} % Location
    {May 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item[] {\textbf{Purchase Order Send-out System Rewrite}}
        \item {Redesigned and rebuilt the purchase order send-out system from a Python/Apache Airflow monolith into a suite of Go microservices orchestrated by GCP Cloud Workflows and Cloud Scheduler, significantly improving reliability and operational visibility.}
        \item {Developed an event-driven purchase order service handling the full order lifecycle with PostgreSQL, gRPC, and GCP Pub/Sub, including pessimistic locking, snapshot-based read consistency, and transactional event publishing.}
        \item {Built a multi-stage replenishment pipeline (load, validate, generate, publish, report) with GCS-persisted state between stages, enabling reliable retry and recovery at any point in the workflow.}
        \item {Implemented multi-format file generation (EDI, XLSX, CSV, XML) with multi-channel distribution (SFTP, FTP, email, Transus EDI platform) to 60+ supplier sites across major partners.}
        \item {Resolved production failures caused by a 100-second execution limit by introducing an asynchronous callback pattern with GCP Workflows, decoupling publish operations from the timeout constraint.}
        \item {Built a configuration management service that dynamically generates GCP Workflow definitions and Cloud Scheduler jobs from supplier configurations, enabling non-engineering teams to onboard new suppliers without code changes.}
        \item {Established comprehensive monitoring with automated detection of failed workflows, missed sendout windows, and unsent order summaries, integrated with Slack and Datadog.}
        \item[] {\textbf{Automated Shelf Placement Optimization}}
        \item {Designed and built an item planning service that automates product-to-hub shelf assignment, combining country-level defaults with hub-specific overrides, physical dimensions, and sales ranking data to group SKUs into placement modules.}
        \item {Developed a shelf mapping and optimization service that computes optimal SKU-to-shelf assignments across warehouse hubs, supporting dynamic mapping file processing, auto-assignment of new products, and a transactional outbox for reliable event publishing.}
        \item {Implementing a multi-objective shelf placement optimizer using Google OR-Tools CP-SAT solver, balancing product demand ranking, space utilization, placement stability, ergonomic shelf height, and accessibility --- deployed as a decoupled HTTP solver service with 3D footprint calculation and module-level isolation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer, Delivery Lead} % Job title
    {apinity GmbH} % Organization
    {Munich, Germany} % Location
    {Dec. 2021 - May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Owned the full lifecycle of microservices powering an API management SaaS platform for the insurance industry --- from design and development through testing, deployment, and ongoing maintenance.}
        \item {Led the migration of inter-service communication from Axon Framework to Apache Kafka and gRPC, improving scalability and decoupling between services.}
        \item {Introduced a centralized observability stack (Spring Boot Actuator, OpenTelemetry, Grafana with Loki and Tempo), significantly reducing mean time to detection and resolution of production incidents.}
        \item {Built fully automated CI/CD pipelines on Azure DevOps for containerized applications using Docker, Azure Container Registry, and Kubernetes.}
        \item {Developed custom Kong Gateway plugins in Go to support platform-specific API routing and authentication requirements.}
        \item {Coordinated a small external engineering team --- collaborated with the Product Owner on backlog refinement, conducted technical reviews, and served as the primary point of contact for escalations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Enmacc GmbH} % Organization
    {Munich, Germany} % Location
    {Nov. 2017 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented RESTful backend services for a professional OTC energy trading platform used by major European energy market participants.}
        \item {Drove adoption of Kubernetes and Apache Kafka, improving system resilience and enabling event-driven processing of trading workflows.}
        \item {Maintained high code quality standards through systematic code reviews, test coverage improvements, and enforcement of engineering best practices.}
        \item {Conducted technical interviews and onboarded and mentored junior engineers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Elinvar GmbH} % Organization
    {Berlin, Germany} % Location
    {Mar. 2017 - Nov. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed the integration subsystem of a WealthTech Platform-as-a-Service, connecting its core portfolio calculation engine with custodian banks, market data feeds, and financial news providers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Market Logic Software AG} % Organization
    {Berlin, Germany} % Location
    {Dec. 2015 - Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented a data ingestion platform for an AI-powered market intelligence product, aggregating content from diverse sources (email, RSS, SOAP/REST APIs, HTML crawling), transforming it, and indexing it into an Elasticsearch cluster for downstream analytics.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Luxoft Poland. Sp. z o.o.} % Organization
    {Wroclaw, Poland} % Location
    {Oct. 2014 - Dec. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed a monitoring tool for Hazelcast cluster memory management with automated eviction of stale data.}
        \item {Implemented MapReduce jobs on Apache Hadoop and developed Apache Spark applications to process large volumes of financial data.}
        \item {Authored Pig scripts for ETL pipelines and contributed to an internal dashboard for real-time job status visualization.}
        \item {Conducted technical interviews for the engineering team.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java Developer} % Job title
    {ISsoft Solutions} % Organization
    {Minsk, Belarus} % Location
    {Aug. 2013 - Oct. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed backend services for a restaurant operations platform, enabling order management and workflow automation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java Developer} % Job title
    {Intetics Co.} % Organization
    {Minsk, Belarus} % Location
    {Aug. 2012 - Aug. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built an analytics system that evaluated users' mobile consumption patterns (SMS, voice calls, data usage) across providers, simulated alternative tariff plans, and recommended cost-optimal options.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Junior Java Developer} % Job title
    {Artezio} % Organization
    {Vitebsk, Belarus} % Location
    {Feb. 2011 - Jun. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a time-tracking web application for internal project management and resource allocation.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
